Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-03-03 Report/dual_approach.tex
final_version_for Antti, Nam, and Markku

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

>>>>

Upon solving \eqref{eqn-dual-3} for \me{\mbfa{\zeta}_b \forall b} in the \me{\ith{i}} iteration, the next iterate is updated by exchanging the corresponding interference terms between two \acp{BS} \me{b} and \me{b_k} as
\begin{equation}
\mbfa{\zeta}_{b_k}(b)^{(i+1)} = \mbfa{\zeta}_{b}(b_k)^{(i+1)} = \frac{\mbfa{\zeta}_{b}(b_k) + \mbfa{\zeta}_{b_k}(b)}{2}.
\label{if-sg-update}
\end{equation}
The dual vector for the next iteration is updated by using subgradient to maximize the dual objective as
\begin{equation}
\mbfa{\nu}_b^{(i+1)} = \mbfa{\nu}_b^{(i)} + \rho \left (\mbfa{\zeta}_b - \mbfa{\zeta}_b^{(i+1)} \right ),
\label{dual-sg-update}
\end{equation}
where the step size parameter \me{\rho} is chosen in accordance with \cite{boyd2011distributed}, which depend on the system model under consideration. The convergence rate of the distributed algorithm is susceptible to the choice of the step size parameter \me{\rho}. For our simulation models, we consider the step size parameter \me{\rho=2}. The above iteration is performed until convergence or for certain accuracy in the variation of the objective value between two consecutive updates. The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l}}
	\KwInit{\me{i=0} and \me{{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{power_update}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} \;
	initialize the interference vectors \me{\mbfa{\zeta}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in\mc{B}} \;
	initialize the dual vectors \me{\mbfa{\nu}^{(0)}_b = \mbfa{0}^{\mathrm{T}}, \forall b \in \mc{B}} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and \me{\mbfa{\zeta}_{b}} with \eqref{eqn-dual-3} using \me{\mbfa{\zeta}^{(j)}_{b}} \;
				exchange \me{\mbfa{\zeta}_{b}} among \acp{BS} in \me{\mc{B}} \;
				update interference vector \me{\mbfa{\zeta}^{(j+1)}_b} using \eqref{if-sg-update}\;
				update dual variables in \me{\mbfa{\nu}^{(j+1)}_b} using \eqref{dual-sg-update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{l,k,n}}\;
			update \me{\mvec{w}{l,k,n}} and notify all \acp{BS} in \me{\mc{B}} using uplink precoded pilots \cite{komulainen2013effective}\;
			update \me{\tilde{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} point or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} operating point \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

### 2015-03-03 Report/simulation_distributed.tex
final_version_for Antti, Nam, and Markku

The performance of the distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. Fig. \ref{fig-d} compares the performance of the algorithms for the system configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the total number of backlogged packets at each \ac{BS}. The total number of queued packets assumed for both figures is \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As pointed out in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-3-2}
	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
	\label{fig-d}
\end{figure}

@@

Fig. \ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents by plotting the total number of backlogged packets at each \ac{SCA} update point. The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one. A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}. It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function. It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure*}
	\centering
	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
		\label{fig-review}
	}
	\hfill
	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 5} bits]{
		\includegraphics[width=0.48\textwidth]{instant_queue_over_time}
		\label{fig-review-time}
	}
	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
	\label{fig-time-analysis}
\end{figure*}

>>>>

The distributed algorithms are compared using the total number of backlogged packets after each \ac{SCA} update points. \review{Fig. \ref{fig-d} compares the performance of the algorithms for the configuration \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} with \me{N_T = 4} transmit antennas at the \acp{BS} with the \ac{PL} varies uniformly between \me{[0,-6]} dB}. Each \ac{BS} serves \me{|\mc{U}_b| = 4} users in a coordinated manner to reduce the number of backlogged packets at each \ac{BS}. The number of queued packets is given by \me{Q_k = [5,7,9,11,8,12,5,4]} bits. As discussed in Section \ref{sec-4}, the performance and the convergence speed of the distributed algorithms are susceptible to the step size used in the subgradient update. Due to the fixed interference levels in the primal approach, it may lead to infeasible solutions if the initial or any intermediate update is not feasible.
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{fig-3-2}
	\caption{Convergence of the centralized and the distributed algorithms for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 3,2,8,1 \rbrace} \review{using \me{\ell_1} norm for \ac{JSFRA} schemes}}
	\label{fig-d}
\end{figure}

@@

\review{Fig. \ref{fig-d-3.1} compares the performance of the centralized and the \ac{KKT} algorithm in Section \ref{sec-4.3} for different exponents with \me{Q_k = [9,16,14,16,9,13,11,12]} bits and the \ac{PL} varies uniformly between \me{[0,-3]} dB}. The \me{\ell_1} norm \ac{JSFRA} scheme provides better performance over other schemes due to the greedy objective. The \ac{KKT} approach for \me{\ell_1} norm is not defined due to the non-differentiability of the objective as discussed in the Section \ref{sec-4.3}. If used for \me{\ell_1} norm, the problem of over-allocation will not affect the dual variables \me{\sigma_{l,k,n}} and \me{\alpha_{l,k,n}} since the queue deviation is raised to the power zero in \eqref{kkt-mse-4.2}, which will always be equal to one. A heuristic method based on subdifferential calculus in \cite{bertsekas1999nonlinear} is proposed in Fig. \ref{fig-d-3.1} by assigning zero for \me{\sigma_{l,k,n}} when the queue deviation is negative, \textit{i.e}, \me{Q_k - t_k < 0}. It is required to address the problem of over-allocation in the \me{\ell_1} norm for dropping the absolute value operator from the objective function. It can be seen that the heuristic method oscillates near the stationary point with the deviation determined by the factor \me{\rho} used in \eqref{kkt-mse-4.1}.
\begin{figure*}
	\centering
	\subfloat[][Average backlogged packets in the system after \me{100} transmission instants]{
		\includegraphics[width=0.48\textwidth]{average_queue_over_time}
		\label{fig-review}
	}
	\hfill
	\subfloat[][Total backlogged packets at each transmission slot for \me{A_k = 5} bits]{
		\includegraphics[width=0.48\textwidth]{instant_queue_over_time}
		\label{fig-review-time}
	}
	\caption{Time analysis of the Queue dynamics for a system \me{\lbrace N,N_B,K,N_R \rbrace = \lbrace 4,2,12,1 \rbrace}}
	\label{fig-time-analysis}
\end{figure*}

### 2015-03-03 Report/simulation_intro.tex
final_version_for Antti, Nam, and Markku

The simulations carried out in this work consider the path loss varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
	\label{fig-a}
\end{figure*}

>>>>

The simulations carried out in this work consider the \ac{PL} varying uniformly across all users in the system with the channels drawn from the \textit{i.i.d.} samples. The queues are generated based on the Poisson process with the average values specified in each section presented. 
\begin{table*}
	\centering
	\caption{Sub-channel-wise listing of channel gains and rate allocations by different algorithms for a scheduling instant}
	\renewcommand{\arraystretch}{1.25} \scriptsize
	\begin{tabular}{|*{14}{c|}}
		\hline
		\multirow{2}{*}{Users} & \multirow{2}{*}{Queued} & \multicolumn{3}{c|}{\multirow{2}{*}{Channel Gains}} & \multicolumn{3}{c|}{Q-WSRME approach} & \multicolumn{3}{c|}{\multirow{2}{*}{JSFRA Scheme}} & \multicolumn{3}{c|}{Q-WSRM band} \\
		\multirow{2}{*}{} & \multirow{2}{*}{Packets} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{(modified \review{\emph{backpressure}})} & \multicolumn{3}{c|}{} & \multicolumn{3}{c|}{Alloc Scheme} \\
		\cline{3-14}
		&& SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} & SC-\me{1} & SC-\me{2} & SC-\me{3} \\
		\hline
		\me{1} & \me{4} & \me{1.71} &  \me{0.53}  &  \me{0.56} & \me{0} &  \me{0}  &  \me{0} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{0} \\
		\me{2} & \me{8} & \me{0.39} &  \me{1.41}  &  \me{1.03} & \me{0} &  \me{4.88}  &  \me{3.11} & \me{0} &  \me{5.49}  &  \me{0} & \me{0} &  \me{4.39}  &  \me{3.53} \\
		\me{3} & \me{4} & \me{2.34} &  \me{1.26}  &  \me{2.32} & \me{4.0} &  \me{0}  &  \me{0} & \me{0} &  \me{0}  &  \me{4.0} & \me{5.81} &  \me{0}  &  \me{0} \\
		\hline
		\multicolumn{5}{|c|}{Remaining backlogged packets (\me{\chi})} & \multicolumn{3}{c|}{\me{3.92} bits} & \multicolumn{3}{c|}{\me{2.51} bits} & \multicolumn{3}{c|}{\me{5.89} bits} \\
		\hline
	\end{tabular}
	\label{tbl-1}
\end{table*}
\begin{figure*}
	\centering
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 4,3,9,4,1\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-1-4}
		\label{fig-1}}
	\subfloat[][System Model \me{\lbrace N,N_B,K,N_T,N_R \rbrace = \lbrace 2,3,9,4,2\rbrace}]{
		\includegraphics[width=0.5\textwidth]{fig-2-5}
		\label{fig-2}}
	\caption{Total number of backlogged packets \me{\chi} present in the system after each \ac{SCA} updates \review{using \me{\ell_1 (q = 1)} norm for \ac{JSFRA} schemes}}
	\label{fig-a}
\end{figure*}

### 2015-03-03 Report/simulation_results.tex
final_version_for Antti, Nam, and Markku

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The path loss between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest path loss component. Fig. \subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

>>>>

For a \ac{MIMO} framework, we consider a system with \me{N=3} sub-channels and \me{N_B = 3} \acp{BS}, each equipped with \me{N_T = 4} transmit antennas operating at \me{10}dB \ac{SNR}, serving \me{|\mc{U}_b| = 3} users each. The \ac{PL} between the \acp{BS} and the users are uniformly generated from \me{[0,-3]} dB and the association is made by selecting the \ac{BS} with the lowest \ac{PL} component. Fig. \subref*{fig-1} shows the performance of the centralized schemes for a single receive antenna system. The total number of queued packets for Fig. \subref*{fig-1} is given by \me{Q_k = [14,15,14,8,12,9,12,11,11]} bits and for Fig. \subref*{fig-2} is \me{Q_k = [9,12,8,12,5,4,10,8,5]} bits respectively.

### 2015-03-03 Report/wsrm_formulation.tex
final_version_for Antti, Nam, and Markku

We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}. The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system. The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint of \eqref{eq:SINR}. Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-6}
	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
\end{IEEEeqnarray}
}
\review{The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation. Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}. \review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}. \review{Since the \ac{JSFRA} formulation can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, it also belongs to the class of NP-hard problems.}

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let us define a function, 
\begin{equation}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}},
\end{equation}
where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. \review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} method in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}

>>>>

\review{We present an iterative algorithm to solve \eqref{eqn-3} by using alternating optimization technique in conjunction with \acf{SCA} \cite{marks1978technical}. The problem is to determine the transmit precoders \me{\mvec{m}{l,k,n}} and the receive beamformers \me{\mvec{w}{l,k,n}} to minimize the total number of backlogged packets in the system. The \ac{SINR} expression in \eqref{eq:SINR} cannot be used to formulate the problem directly due to the equality constraint of \eqref{eq:SINR}. Using additional variables, we relax the expression \eqref{eq:SINR} by inequality constraints to solve \eqref{eqn-3} as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{CCl}\label{eqn-6}
\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\ \beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} & \quad & \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \\
\text{subject to}& \quad &\gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}  |^2}{\beta_{l,k,n}} \IEEEyessubnumber \label{eqn-6.2} \\
  & \quad & \beta_{l,k,n} \geq  \enoise + \hspace{-0.75em} \sum_{(j,i) \neq (l,k)} \hspace{-0.75em} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \label{eqn-6.3} \\
  & \quad & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \label{eqn-6.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CCl} \label{eqn-6}
	\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n},\\\beta_{l,k,n},\mvec{w}{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}  \|_q \label{eqn-obj} \IEEEyessubnumber \vspace{-0.25cm}\\
	\text{subject to} &\quad& \gamma_{l,k,n} \leq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}} \IEEEyessubnumber \eqspace \label{eqn-6.2} \\
	&\quad& \beta_{l,k,n} \geq \enoise + \sum_{\mathclap{(j,i) \neq (l,k)}} |\mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \IEEEyessubnumber \eqspace \label{eqn-6.3} \\
	&\quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}}, \fall b. \IEEEyessubnumber \eqspace \label{eqn-6.4}
\end{IEEEeqnarray}
}
The \ac{SINR} expression in \eqref{eq:SINR} is relaxed by the inequalities \eqref{eqn-6.2} and \eqref{eqn-6.3} in the above formulation. Note that \eqref{eqn-6.2} is an under estimator for \ac{SINR} \me{\gamma_{l,k,n}}, and \eqref{eqn-6.3} provides an upper bound for the total interference seen by user \me{k \in \mathcal{U}_b}, denoted by the variable \me{\beta_{l,k,n}}}. \review{The constraints are tight when each \ac{BS} objective is non zero at the optimal point, as discussed in Appendix \ref{a-3}}. \review{Since the \ac{JSFRA} formulation can be modeled as a \ac{WSRM} problem, which is known to be NP-hard \cite{np_hard}, it also belongs to the class of NP-hard problems.}

In order to find a tractable solution for \eqref{eqn-6}, we note that \eqref{eqn-6.4} is the only convex constraint with the involved variables. Thus, we only need to deal with \eqref{eqn-6.2} and \eqref{eqn-6.3}. We resort to the \ac{AO} technique by fixing the linear receivers, to solve for the transmit beamformers. For a fixed receivers \me{\mvec{w}{l,k,n}}, the problem now is to find the optimal transmit beamformers \me{\mvec{m}{l,k,n}} which is still a challenging task. We note that for a fixed \me{\mvec{w}{l,k,n}}, \eqref{eqn-6.3} can be written as a \ac{SOC} constraint. Thus, the difficulty is due to the non-convexity of the \ac{DC} constraint in \eqref{eqn-6.2}. Let us define a function, 
\begin{equation}
f({\mbf{u}}_{l,k,n}) \triangleq \frac{ | \mvec{w}{l,k,n}^\herm \mvec{H}{l,k,n} \mvec{m}{l,k,n}|^2}{\beta_{l,k,n}},
\end{equation}
where \me{{\mbf{u}}_{l,k,n} \triangleq \{\mvec{w}{l,k,n}, \mvec{m}{l,k,n},\beta_{l,k,n}\}} is the vector which needs to be identified for the optimal allocation. Note that the function \me{f({\mbf{u}}_{l,k,n})} is convex for a fixed \me{\mvec{w}{l,k,n}}, since it is in fact the ratio between a quadratic form of \me{\mvec{m}{l,k,n}} over an affine function of \me{\beta_{l,k,n}} \cite{boyd2004convex}. \review{The nonconvex set defined by the \ac{DC} constraint \eqref{eqn-6.2} can be decomposed by a series of convex subsets by linearizing the convex function \me{f({\mbf{u}}_{l,k,n})} with its first order Taylor approximation around a fixed operating point \me{\tilde{\mbf{u}}_{l,k,n}} \cite{lipp2014variations,lanckriet2009convergence}, also called as \ac{SCA} approach in \cite{marks1978technical}. By using the reduced convex subset for \eqref{eqn-6.2}, the problem defined in \eqref{eqn-6} can be solved at each operating point iteratively.}
